Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-25 paper/paper.tex
proofread from page 6 on, not including Autopilot specs or safety.

\documentclass[pdftex,10pt,letter]{article}
\usepackage[pdftex]{graphicx}
\usepackage[left=1.5in, right=1.5in, top=1.25in, bottom=1.25in]{geometry}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=blue
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\itemspace}{	\setlength{\itemsep}{0cm} \setlength{\parskip}{0cm}}
\newcommand{\degrees}[1]
{
\begin{math}
#1^{\circ} 
\end{math}
}
\hyphenation{auto-nomous construction}

@@

\section{Introduction}

The Rutgers Autonomous Aircraft Team was formed in September 2008 with the goal of entering the 2009 Association for Unmanned Vehicle Systems International (AUVSI)\cite{auvsiweb} Unmanned Air Systems (UAS) competition\cite{uasweb}. We didn't make it to the 2009 competition after losing our aircraft only four weeks before. Our imaging system and autopilot system were also far from ready. In terms of NCAA sport eligibility, one could consider 2009 our `red shirt' year. In 2010 we are still rookies.

@@

We are advised by
 Professor Tobias Rossmann,
 and several members of the Tri-County R/C Club \cite{tricountyRC}:
 Larry Kosinar,
 Bill Perkowski,
Chris Eivan,
and  Mike Korb, 
amongst many who spent time mentoring us.

We have been generously funded by 
Rutgers Engineering Governance Council,
Rutgers Alumni Association,
WINLAB, a laboratory of the Rutgers University Department of Electrical Engineering, 
and BP Hobbies.

We would like to acknowledge
Louis Stumpf, for donating the aircraft that became the \emph{Daedalus};
Jeff Perkins, for his prolific networking and promotion of the team;
Gregg Peters of BP Hobbies for getting us out of numerous binds;
Dave Devries and Michael Maia, of Invensense, for their technical guidance;
Professor Chung-chieh Shan, for overseeing Pat's independent study on the IMU design;
Ivan Seskar, for keeping us (and many other undergrads) in the black; and
Roger Kondos and Brij Pathak, for contributing to the thermopile attitude sensor.

\begin{figure}[b!]
	\centering
	\includegraphics[width=0.75\textwidth]{../images/wreckage.jpg}
	\caption{The recovery of our 2009 entry, the \emph{Icarus}}
	\label{fig:wreckage}
\end{figure}

\newpage
\section{Systems Engineering}
\subsection{Goals}
For this entry we took a close look at our goals and requirements, and attempted to meet the ``threshold'' competition requirements successfully.
We started the design by forming, as a team, some broad goals based on our experience in the 2009 competition.
These goals allowed sub-teams and individuals to tackle the smaller problems while still keeping an eye on the big picture.

We also wanted to balance building components with buying components, keeping in mind our slim finances. While we couldn't build every part of our entry from scratch, we were motivated to build as much of our systems as possible for the learning experience. We tried to buy only components which we didn't have the time or resources to build ourselves.

@@

\begin{itemize}
	\item The air vehicle must be stable and slow, with ample payload capacity and 20 minute flight duration. It should be a proven and durable fixed-wing design.
	\item The autopilot must be based on a proven system, so we could focus on improving an existing system rather than reinventing the wheel. It also must be open-source, both because of the high cost commercial systems, and because we want to learn about and experiment with the internals of our autopilot system.
	\item The imaging system must be simple and capable. We assume the operator will be burdened with guiding the camera and identifying targets manually. We couldn't guarantee time and resources would permit us to add sensor information and control loops for camera guidance and computer vision for target identification.
\end{itemize}

We will be performing a manual take off and giving the autopilot system control of the aircraft once the plane is in the air. We will also perform a manual landing. We decided not to pursue the reach goals of autonomous takeoff and landing based on our inexperience and the risk of a crash during development.
\subsection{System Design Decisions}
\subsubsection{Airframe System Engineering}

@@

One of the most difficult design decisions was to quantify ``ample payload.'' Payload size and weight is the major determining factor in aircraft size.  We originally assumed a 2.5lb electronics (flight computer, sensors, and batteries) payload and a 2.5lb pan-tilt camera 8'' in diameter, requiring 6'' of vertical space below the bottom of the aircraft. These considerations introduced two major design parameters: the aircraft must be capable of carrying a minimum 5lb payload, and must be situated to provide clearance for the pan tilt unit.

We also needed an easily controllable, stable platform to accommodate the autopilot, and we needed to keep flight speed low to make image capture as easy as possible. After consulting with R/C experts, a high wing trainer is looked like the most stable and proven fixed-wing design. Trainers traditionally have light wing loading for slow speed flight, and are able to carry a comparatively large payload.Their lower wing loading is easier to control, and easier to recover if power is lost.

Erring on the side of caution, we decided our aircraft should be capable of accommodating a worst-case scenario payload. 
We were, in part, cautious due to a previous error where we rebuilt an entire aircraft to accommodate a larger payload.
We decided on a high wing trainer with a 10' to 12' wingspan, so that we could accommodate up to 5lbs of payload while maintaining suitable wing loading.
Though we managed to keep our payload weight well under 5lbs, the only major drawback to having an oversize aircraft is the difficulty of transport.

Our selection of a trainer type aircraft encouraged us to rethink our pan tilt design. We based our initial assumptions of an 8'' diameter pan and tilt unit, mounted underneath the aircraft, based on a design that was to be mounted on the nose of our 2009 entry, an aircraft with a pusher motor configuration. When we considered the possibilities of either dramatically increasing the ride height of our aircraft, or making significant modifications to the width of the fuselage, we decided to redesign our pan tilt system to fit in a more suitable envelope.

@@

We had sketched plans for an electronics system built entirely on a Linux-based flight computer as early as July 2009, but planned on using a more standard microcontroller-based autopilot system with an auxiliary Linux-based computer for the imaging system until December 2009. After burning out our microcontroller based autopilot for the second time, we were faced with a long lead time for an expensive replacement part. On that impetus, we redesigned our electronics systems to eliminate the microcontroller autopilot and ensure all of our replacement parts would be inexpensive and commercially available from many vendors. The move to a single Linux-based flight computer, while not without obstacles, was a successful design decision, as we'll describe in this paper.

@@

We felt the Paparazzi system was full featured and proven, but we weren't satisfied with the capabilities of the existing Paparazzi hardware. The ``Tiny'' v2.1\cite{paparazzi_tinyv21}, the latest autopilot hardware released by the Paparazzi project, is based on a 64 pin ARM microcontroller. Almost all of its input-output capabilities are dedicated to autopilot functions, making it difficult to expand functionality and share information (for instance, position and orientation estimates) with payload components. As previously stated, the Tiny is expensive, fragile\footnote{In our own admittedly clumsy experience} and often subject to long lead times.

@@

We elected to take many steps in the software engineering to help ensure our flight computer will operate reliably. The most important of these was code review and incremental testing. Both Pat Hickey and Bradley Lord became intimately familiar with the source code and control flow inside the autopilot software, and all patches were reviewed and tested by both engineers. Numerous other safety measures are described in Section \ref{sec:autopilot_software}.

Because our entry is essentially an experimental system and will always be operated with a safety pilot present, we engineered the safety pilot override to operate independently from the flight computer. We have ensured that, short of losing power to the radio control receiver and servos, the safety pilot will always be able to take over with the flick of a single switch on his radio control transmitter. We have also ensured that the flight computer's servo controller will be able to detect a loss of computer control and servos to a recoverable default. Along with careful preflight testing, careful observation, and definitive analysis of any errors encountered during flight, these measures meet the spirit and letter of competition rules.

@@

When designing the imaging system our major goals were to have 
1) a camera able to capture imagery ``up to \degrees{60} in all directions from vertically below the aircraft''\cite{competition_rules}, as per the rules; 
2) a real-time video feed;
4) the ability to download pictures while in flight; and
3) the ability to remotely control the camera, particularly to trigger pictures.

It was difficult to find a camera to base our imaging system on which met all of these requirements. Many still cameras can be fitted on a pan tilt system to requirement 1, and provide a real-time ``viewfinder'' video feed to meet requirement 2. Requirement 3 could typically be managed by attaching the camera to a single board computer by USB cable, though usually the camera powers down when attached to the computer, and some sort of switch is needed to deactivate the USB cable once the data transfer is complete.

Requirement 4 had the greatest effect on our design decision. Typically, only high-end SLR-type still cameras provide a socket for remote control. These are beyond our price range, and are much larger and heavier than we would like.

We built a prototype using a Canon Powershot S3 IS \cite{powershotS3}, a camera which has no electrical remote control input. We soldered wires to the push-button pads for the shutter and zoom buttons so we could override them remotely. Those wires were attached to isolating transistors, and a microcontroller was used for control. After some time, this clever circumvention of the factory anti-static shielding resulted in a burnt out camera. We abandoned this scheme.

@@

At the time of this writing, we have completed and flown a single flight vehicle, which we have named the \emph{Daedalus}.
We have also nearly completed a very similar backup airframe which will serve as a backup in case the \emph{Daedalus} has a disaster. The \emph{Knight Two} will be fitted with nearly identical R/C flight electronics, and accept the same autopilot and imaging system payload as the \emph{Daedalus}.

@@

\subsubsection{Daedalus}
\begin{wrapfigure}{l}{0.4\textwidth}
	\includegraphics[width=0.37\textwidth]{../images/daedalus_isometric.jpg}
	\caption{The \emph{Daedalus}}
	\label{fig:daedalus}
\end{wrapfigure}
Louis Stumpf, a member of our local R/C club, donated a 10ft 1in (3.07m) wingspan, 7ft 8in (2.33m) long, high wing trainer to our club. It met all of the requirements outlined previously.

The plane, first built out of foam and balsa from long-lost plans in 1986, was accepted graciously, but required quite a bit of work before it was once again flight-worthy. We removed the covering to find water damage and rot which resulted from years of storage. We stripped and rebuilt nearly the entire airframe, adding carbon-fiber reinforcements to the wing in anticipation of increased wing loading due to our payload. Once rebuilt and covered,  the \emph{Daedalus} weighed 19.5 lbs with engine. A full 24oz fuel tank, plus 3.5 lbs electronics payload, would bring the maximum takeoff weight to 25.5lbs.

We wanted to certify the wings and wing root would withstand large dynamic forces in flight. 
We designed a test to mimic the 
Federal Airworthiness Standards' structural requirements\footnote{Special Federal Aviation Regulation No. 23, Subpart C--Structure. Assuming full load on wing as described in 23.335 paragraph 4.i., where an aircraft must pull out of a \degrees{7.5} dive at cruise velocity and cruise power ``with a load factor of 1.5 (0.5$g$. acceleration increment)'' \cite{far23}}. Our first test was designed to certify that the wing, supported at the wing root and fuselage, could take a bottom loading present in a 1.5$g$ acceleration, with a safety factor of 1.5\footnote{As stated in 23.303 \cite{far23}.}.

@@

Satisfied, we made engine and surface tests (see \ref{sec:appendix_preflight}) before taxiing the plane around a parking lot.  We brought the plane back inside, examined it for signs of stress and, finding everything in good condition, deemed the \emph{Daedalus} flight-worthy.

@@

In order to mitigate a disaster such as we had last year, we decided to build another airframe which could replace the \emph{Daedalus} at short notice. We selected an Aero-Design 12 Foot Telemaster \cite{aerodesign} because it was available as a balsa kit and similar in size to the \emph{Daedalus}. The 12 Foot Telemaster has a 12ft 1in (3.68m) wingspan, and is 7ft 10in (2.38m) in length.We named it the \emph{Knight Two} after the Rutgers University mascot, the Scarlet Knight.

At the time of this writing, the \emph{Knight Two} is 85\% complete. We plan to complete the aircraft and bring it to the competition as a spare.  
Since our testing plan for the \emph{Daedalus} was successful, we will follow the same plan when the \emph{Knight Two} is completed.

@@

\subsection{Safety Features}
Our system is designed to gracefully handle any failure while continuing to ensure the safety of those nearby. 
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item The channel 5 toggle switch determines whether the radio control transmitter, or the autopilot, has control over the flight control servos. The radio control safety pilot may disengage the autopilot at any time by flicking this switch.
	\item If the plane loses telemetry with the ground station for more than 10 seconds, the autopilot will default to a ``return home mode'' that will direct the plane towards the ground station in hopes of reestablishing a connection.  
	\item If the connection telemetry remains dead for 30 seconds, the autopilot will bring the servos to a predefined default (throttle closed, elevator up, rudder right, ailerons left). The servos will remain in that position until the safety pilot takes control of the aircraft.
	\item If the flight computer does not provide the servo controller with a new servo output value for longer than 2 seconds, the servo controller will bring the servos to a predefined default (throttle closed, elevator up, rudder right, ailerons left).  The servos will remain in that position until the safety pilot takes control of the aircraft.
	\item During engine start, the centerman (see \ref{appendix_preflight}) may kill the engine at any time with the ignition switch located on the right side of the aircraft, behind the engine mount.
	\item Radio control channel 6 functions as a remote kill switch on the \emph{Knight Two}, disengaging the electronic ignition system of the engine. (The \emph{Daedalus} has a magneto ignition, so we only have the manual kill switch behind the engine mount)
\end{itemize}

@@

\newpage

\bibliographystyle{plain}
%\renewcommand{\refname}{\section{Citations}}
\bibliography{paper}

The \LaTeX$\,$ source and figures of this paper are available on github:

\url{http://github.com/pchickey/ruaiaa-2010doc/}

>>>>

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage[left=1.5in, right=1.5in, top=1.25in, bottom=1.25in]{geometry}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=blue
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\itemspace}{	\setlength{\itemsep}{0cm} \setlength{\parskip}{0cm}}
\newcommand{\degrees}[1]
{
\begin{math}
#1^{\circ} 
\end{math}
}
\hyphenation{auto-nomous construction}

@@

\section{Introduction TWO}

The Rutgers Autonomous Aircraft Team was formed in September 2008 with the goal of entering the 2009 AUVSI UAS competition. We didn't make it to the 2009 competition after loosing our aircraft only four weeks before. Our imaging system and autopilot system were also far from ready.

In terms of NCAA sport eligibility, one could consider 2009 our `red shirt' year. In 2010 we are still rookies.

@@

We are advised by
 Professor Tobias Rossmann,
 and several members of the Tri-County R/C Club \cite{tricountyRC}:
 Larry Kosinar,
 Bill Perkowski,
and  Mike Korb, 
%and Chris (test pilot) 
amongst many who spent time mentoring us.

We have been generously funded by 
Rutgers Engineering Governance Council,
Rutgers Alumni Association, and
WINLAB, a laboratory of the Rutgers University Department of Electrical Engineering.
% What was Chris Brocco's Uncle's Company? Something Automation?
BP Hobbies,

We would like to acknowledge
Louis Stumpf, for donating the aircraft which became the \emph{Daedalus};
Jeff Perkins, for his prolific networking and promotion of the team;
Gregg Peters of BP Hobbies for getting us out of numerous binds;
Dave Devries and Michael Maia, of Invensense, for their technical guidance;
Professor Chung-chieh Shan, for overseeing Pat's independent study on the IMU design;
Ivan Seskar, for keeping us (and many other undergrads) in the black;
Roger Kondos and Brij Pathak, for contributing to the thermopile attitude sensor.

\begin{figure}[b!]
	\centering
	\includegraphics[width=0.6\textwidth]{../images/wreckage.jpg}
	\caption{The recovery of our 2009 entry, the \emph{Icarus}}
	\label{fig:wreckage}
\end{figure}

\newpage
\section{Systems Engineering}
\subsection{Goals}
For this entry, we took a close look at our goals and requirements, and dialed back our approach to ensure we would meet the most basic competition requirements successfully.
We started the design by forming, as a team, some broad goals based on our experience in the 2009 competition.
These formed the basis on which sub-teams and individuals tackled the smaller problems while still keeping an eye on the big picture.

We also wanted to balance building with buying, keeping in mind our slim finances. While we couldn't build every part of our entry from scratch, we tried to build whatever we could given the 16th June competition deadline.

@@

\begin{itemize}
	\item The air vehicle must be stable and slow, with ample payload capacity and 20 minute flight duration. It should be a proven and durable fixed-wing design.
	\item The autopilot must be based on a proven system, so we could focus on improving an existing system rather than reinventing the wheel. It also must be open-source, both because of the high cost commercial systems, and because we want to learn about and experiment with the internals of our autopilot system.
	\item The imaging system must be simple and capable. We assume the operator will be burdened with guiding the camera and identifying targets until time and resources permit us to add sensor information and control loops for guidance, and computer vision for identification. It will be custom built, because we could not find any affordable systems available commercially.
\end{itemize}

We made design decisions of which competition goals we will attempt. 
We will be performing a manual take off, and giving the autopilot system control of the aircraft once the plane is in the air. We will also perform a manual landing. We decided not to pursue the reach goals of autonomous takeoff and landing based on our inexperience and the risk, during development and competition, to our aircraft.
\subsection{System Design Decisions}
\subsubsection{Airframe System Engineering}

@@

The teams made design decisions based on the aforementioned competition goals.

One of the most difficult design decisions was to quantify ``ample payload.'' Payload size and weight is the major determining factor in aircraft size.  We originally assumed a 2.5lb electronics (computer + batteries) payload and a 2.5lb pan-tilt camera 8'' in diameter, requiring 6'' of vertical space extruding from the bottom of the aircraft. These considerations introduced two major design parameters: the aircraft must be capable of carrying a minimum 5lb payload, and must be situated to provide clearance for the pan tilt unit.

Additionally, we sought an easily controllable, stable platform to accommodate the autopilot, and an ability to fly at low speeds, in order to more easily capture clear images.

We determined, after consulting with R/C experts, that a high wing trainer is the most stable and proven fixed-wing design. Trainers traditionally have light wing loading for slow speed flight, and are able to carry a comparatively large payload. Additionally, a large plane with lower wing loading is easier to control, and easier to recover if power is lost. Consciously agreeing to err on the side of caution, we sought a large plane capable of accommodating a worst-case scenario payload, and settled on a wingspan on the order of 10'-12'. Though lighter and smaller payload alternatives were found as the year progressed, these merely leave us with more freedom for future modifications.
%That last sentence sounds kind of eh, I'm stuck on a decent wording, so I'm leaving it for now.

The decision to employ a large, high wing trainer, however, forced us to rethink our original pan-tilt design. Last year, in order to accommodate the pan-tilt unit, we designed a pusher plane, enabling us to mount the pan-tilt under the plane's nose, which had sufficient clearance. Since trainers are generally designed with front-mounted engines (I presume?), we were forced to engineer a new solution requiring significantly less clearance. In the long run, we modified the pan-tilt mount to allow us to recess more of the pan-tilt unit into the body of the plane---this had the added benefit of providing more protection to an expensive piece of equipment on takeoff and landing.

@@

We had sketched plans for an electronics system built entirely on a Linux-based flight computer as early as July 2009, but planned on using a more standard microcontroller-based autopilot system with an auxillary Linux-based computer for the imaging system until December 2009. After burning out our microcontroller based autopilot for the second time, we were faced with a long lead time for an expensive replacement part. On that impetus, we redesigned our electronics systems to eliminate the microcontroller autopilot and ensure all of our replacment parts would be inexpensive and commercially available from many vendors. The move to a single Linux-based flight computer, while not without obstacles, was a successful design decision, as we'll describe in this paper.

@@

We felt the Paparazzi system was full featured and proven, but we weren't satisified with the capabilities of the existing Paparazzi hardware. The ``Tiny'' v2.1\cite{paparazzi_tinyv21}, the latest autopilot hardware released by the Paparazzi project, is based on a 64 pin ARM microcontroller. Almost all of its input-output capabilities are dedicated to autopilot functions, making it difficult to expand functionality and share information (for instance, position and orientation estimates) with payload components. As previously stated, the Tiny is expensive, fragile\footnote{In our own admittedly clumsy experience} and often subject to long lead times.

@@

We elected to take many steps in the software engineering to help ensure our flight computer will operate reliably. The most important of these was code review and incremental testing. Both Pat Hickey and Bradley Lord became intimately familiar with the source code and control flow inside the autopilot software, and all patches were reviewed and tested by both engineers. Numerous other safety measures will be described in Section \ref{sec:autopilot_software}.

Because our entry is essentially an experimental system, and will always be operated with a safety pilot present, we engineered the safety pilot override to operate independently from the flight computer. We have ensured that, short of losing power to the radio control receiver and servos, the safety pilot will always be able to take over with the flick of a single switch on his radio control transmitter. We have also ensured that the flight computer's servo controller will be able to detect a loss of computer control and servos to a recoverable default. Along with careful preflight testing, careful observation, and definitive analysis of any errors encountered during flight, these measures meet the spirit and letter of competition rules.

@@

When designing the imaging system our major goals were to have 1) a camera with XXX range of motion.  2) real-time video feed from the plane.  3) ability to control the camera in real-time and take pictures.  4) ability to download pictures while in flight.  For the camera we chose the Sony Bloggie \cite{bloggie} because it was small, light, cheap, and took high resolution images and video.  In addition it came with a built in rotating lens, which simplified the construcion of the pan-tilt unit, and it can also be controlled remotely over usb, so it interfaced with our flight linux computer.  To communicate with the plane we developed custom ground station software to meet our needs and installed two sets of radios, one for the video feed, and another for communicating with the plane and downloading images.  These radios are independent from the set of radios used for the autopilot because we didn't want to have dependencies between the two systems.

@@

At the time of this writing, we have completed and flown a single flight vehicle, which we have named the \emph{Daedalus}.
We have also nearly completed a very similar backup airframe which serve as a backup in case the \emph{Daedalus} has a disaster. The \emph{Knight Two} will be fitted with nearly identical R/C flight electronics, and accept the same autopilot and imaging system payload as the \emph{Daedalus}.

@@

We elected to pursue a kit-type airplane rather than our own design. 
Our own custom design, the \emph{Icarus}, suffered a catastrophic structural failure last year. From this, we learned that custom structures require much more testing and revision than a proven kit. We also reconsidered our payload requirements and decided we could easily modify a kit plane to accept our autopilot and imaging system.

\subsubsection{Daedalus}
\begin{wrapfigure}{l}{0.4\textwidth}
	\includegraphics[width=0.37\textwidth]{../images/daedalus_isometric.jpg}
	\caption{The \emph{Daedalus}}
	\label{fig:daedalus}
\end{wrapfigure}
A member of our local R/C club, Tri-County RC \cite{tricountyRC}, donated a ten-foot wingspan high wing trainer to our club. The plane, first built out of foam and balsa from long-lost plans in 1986, was accepted graciously, but required quite a bit of work before it was once again flight-worthy. We removed the covering to find water damage and rot which resulted from years of storage. We stripped and rebuilt nearly the entire airframe, adding carbon-fiber reinforcements to the wing in anticipation of increased wing loading due to our payload. Once rebuilt and covered, we tested the \emph{Daedalus} weighed 19.5 lbs with engine. A full 24oz fuel tank, plus 3.5 lbs electronics payload, would bring the maximum takeoff weight to 25.5lbs.

We wanted to certify the wings and wing root would withstand large dynamic forces in flight. 
We designed a test similar to mimic the 
Federal Airworthiness Standards' structural requirements\footnote{Special Federal Aviation Regulation No. 23, Subpart C--Structure. Assuming full load on wing as described in 23.335 paragraph 4.i., where an aircraft must pull out of a \degrees{7.5} dive at cruise velocity and cruise power ``with a load factor of 1.5 (0.5$g$. acceleration increment)'' \cite{far23}}. Our first test was designed to certify that the wing, supported at the wing root and fuselage, could take a bottom loading present in a 1.5$g$ acceleration, with a safety factor of 1.5\footnote{As stated in 23.303 \cite{far23}.}.

@@

Satisfied, made engine and surface tests (see \ref{sec:appendix_preflight}) before taxiing the plane around a parking lot.  We brought the plane back inside, examined it for signs of stress and, finding everything in good condition, deemed the \emph{Daedalus} flight-worthy.

@@

In order to mitigate a disaster such as we had last year, we decided to build another airframe which could replace the \emph{Daedalus} at short notice. We selected an Aero-Design 12 Foot Telemaster \cite{aerodesign} because it was available as a balsa kit and similar in size to the \emph{Daedalus}.

We named it the \emph{Knight Two} after the Rutgers University mascot, the Scarlet Knight. We may rename it if someone can think of a better name. Pat needed to think up a decent name real fast in order to make this rough draft.

Since our testing plan for the \emph{Daedalus} was successful, we will follow the same plan when, in the coming weeks, we finish building \emph{Knight Two}.

Someone please detail the outer dimensions. The inner dimensions, space used for flight electronics, space used for payload underneath. Landing gear height. Number of servos and their locations

Figure may go here: Line drawing of Knight Two. JOHN

@@

\subsection{Safety Features}
Our system is designed to gracefully handle any failure while continuing to ensure the safety of those nearby. 
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Channel 5 (?) allows quick switch to safety pilot in case of autopilot malfunction.
	\item If the plane loses contact with the ground station for more than XX seconds, the autopilot will default to a ``return home mode'' that will direct the plane towards the ground station in hopes of reestablishing a connection.  If the connection remains dead for XX minutes, the autopilot will direct the plane to [DO SOMETHING?]
	\item Channel 6 (?) functions as a remote kill switch, ensuring the ability to cut power to the engine if an emergent situation precludes direct manual shut off.
	\item etc?
\end{itemize}

@@

\bibliographystyle{plain}
%\renewcommand{\refname}{\section{Citations}}
\bibliography{citations}
